---
title: "Data Import"
output: github_document
---

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)
```

## Import FAS Litters CSV

```{r}

litters_df = read_csv("data/FAS_litters.csv")

litters_df = janitor:: clean_names(litters_df) #To only use the library in one line of code so library:: function (ie clean_names() is from library janitor and janitor is not imported into whole code)

head(litters_df)
tail(litters_df, 10)
```

## Learning Assessment

Import data using relative paths

```{r eval=FALSE}

pups_df = read_csv("data/FAS_pups.csv")
pups_df = janitor:: clean_names(pups_df)
```

Importing data using absolute paths will break the path everytime you move files. Use relative paths!!!


## Look at read_csv option


Skip rows using skip (1 indicates skip first row, 2 means skip first 2 rows, etc.)


```{r}

litters_df = read_csv (
            file = "data/FAS_litters.csv",
            skip = 1
)
```

Define what values make the cells empty by using na ()

```{r}

litters_df = read_csv (
            file = "data/FAS_litters.csv",
            na = c("NA", "", ".")
)
```

Change the column variable as a factor variable

```{r}

litters_df = read_csv (
            file = "data/FAS_litters.csv",
            na = c("NA", "", "."),
            col_types = col(
              Group = col_factor()
            )
)
```
